rgbif: R client for working with GBIF species occurrence data

### 2015-10-28 manuscript.tex
update description about datasets, orgs, netowrks, inst, etc., thanks tim

The relationship between these five things is XXXXXX.

@@

Dataset metrics are another useful way of digging in to figure out what
datasets you may want to use. One drawback is that these data are only
available for datasets of type \emph{checklist}, but there are quite a
lot of them (2472).

>>>>

Datasets are owned by organizations. Organizations are endorsed by nodes
to share datasets with GBIF. Datasets are published through
institutions, which may be hosted at another organization. A network is
a group of datasets (managed by GBIF).

@@

Dataset metrics are another useful way of digging in to figure out what
datasets you may want to use. One drawback is that these data are only
available for datasets of type \emph{checklist}, but there are quite a
lot of them (2474).
